---
title: "writing_functions"
author: "Tara Ahi"
date: "11/4/2021"
output: html_document
---

```{r}
library(tidyverse)
library(rvest)
```


## Z Scores

```{r}
x_vec = rnorm(25, mean = 5, sd = 3)

(x_vec - mean(x_vec)) / sd(x_vec)
```


Give me some factor that will return the z score of the number I give

```{r}
z_scores = function(x) {
  
  z = (x - mean(x)) / sd(x)
  z
  
}

z_scores(x_vec)

y_vec = rnorm(40, mean = 12, sd = .3)

z_scores(x = y_vec)
```


How cool is this?

```{r, error=TRUE}
z_scores(3)

z_scores(c("my name is jeff"))

z_scores(mtcars)

```

These don't work, let's try again. Conditional execution:

```{r}
z_scores = function(x) {
  
  if (!is.numeric(x)) {
    stop("x should be numeric")
  } else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
  z = mean(x) / sd(x)
  
  return(z)
}
```

Now check error messages

```{r, error=TRUE}
z_scores(3)

z_scores(c("my name is jeff"))

z_scores(mtcars)

```



```{r, error=TRUE}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  list(mean = mean_x, 
       sd = sd_x)
}

output_df = 
  tibble(
    mean = mean_x,
    sd = sd_x
  )

return(output_df)

mean_and_sd(x_vec)
mean_and_sd(y_vec)
```

x doesn't exist yet so you can go to the console and say `x = y_vec`

## Different sample sizes, means, sds

```{r}
sim_data = tibble(
  x = rnorm(30, mean = 2, sd = 3)
)

sim_data %>% 
  summarize(
    mu_hat = mean(x),
    sigma_hat = sd(x)
  )
```


Let's write a function that simulates data, computes the mean and sd. 

```{r}
sim_mean_sd = function(n, mu, sigma) {
  
  #do checks on inputs
  
  sim_data = tibble(
  x = rnorm(30, mean = 2, sd = 3)
)
  
  sim_data %>% 
  summarize(
    mu_hat = mean(x),
    sigma_hat = sd(x)
  )
  
  
}

sim_mean_sd(30, 4, 3)
```



Looking back at this



```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```

Ok bu there are lots of pages of reviews, let's make a function to look at reviews based on page url

```{r}
read_page_reviews <- function(url) {
  
  html = read_html(url)
  
  review_titles = 
    html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()
  
  review_text = 
    html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim()
  
  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
}
```

